Is high social class always beneficial for survival? A study of adults and elderly in Northern Sweden 1851--2013

### 2017-08-29 CreateData/creDat2.Rnw

\title{Creating Data for "Social inequality in mortality among
  adults and elderly in northern Sweden 1850--2013"\footnote{Version 2017-05-27.}}

@@

\subsection{POPLINK data, 1851--1950}

The POPLINK data cover 1901--1950. A covariate {\tt period} is added and used for splitting the data into calendar time periods of length 10 years each.

<<getdata>>=
source("calWin.R")
calWin
library(xtable)
library(knitr)
library(eha)
library(skum)
library(dplyr)
library(tidyr)
library(stringr)
load("../../Data/adult.rda")
adult <- calWin(adult, c(1851, 1951))
source("R/addPer.R")
addPer
adult <- addPer(adult, cuts = seq(1851, 1951, by = 25))
adult <- rc(adult)
## NEW hisclass, 6 + 7 --> 6:
##adult$hisclass[!is.na(adult$hisclass) & (adult$hisclass == 7)] <- 6
## Recode to four classes:
##New Hisclasses:
ett <- with(adult, !is.na(socBranch) &
                ((socBranch == "official" & socStatus == "high") |
                     (socBranch == "business" & socStatus == "high")
                ))
##tva <- with(adult, !is.na(socBranch) &
  ##              ((socBranch == "farming" & socStatus == "high") |
##                     (socBranch == "business" & socStatus == "low")
##                ))
##tre <- with(adult, !is.na(socBranch) &
##                    (socBranch == "official" & socStatus == "low")
##               )
tva <- with(adult, !is.na(socBranch) &
                ((socBranch == "farming" & socStatus == "high") |
                 (socBranch == "business" & socStatus == "low") |
                 (socBranch == "official" & socStatus == "low")
                ))

@@

>>>>

\title{Creating Data for "Social inequality in mortality among
  adults and elderly in northern Sweden 1801--2013"\footnote{Version 2017-08-27, with a longer time period.}}

@@

\subsection{POPLINK data, 1801--1950}

In this version, we start at 1801-01-01. The POPLINK data cover 1801--1950. A covariate {\tt period} is added and used for splitting the data into calendar time periods of length 10 years each.

<<getdata>>=
source("calWin.R")
calWin
library(xtable)
library(knitr)
library(eha)
library(skum)
library(dplyr)
library(tidyr)
library(stringr)
load("../../Data/adult.rda")
adult <- calWin(adult, c(1801, 1951))
source("R/addPer.R")
addPer
adult <- addPer(adult, cuts = seq(1801, 1951, by = 25))
adult <- rc(adult)
## NEW hisclass, 6 + 7 --> 6:
##adult$hisclass[!is.na(adult$hisclass) & (adult$hisclass == 7)] <- 6
## Recode to four classes:
##New Hisclasses:
ett <- with(adult, !is.na(socBranch) &
                ((socBranch == "official" & socStatus == "high") |
                     (socBranch == "business" & socStatus == "high")
                ))
##tva <- with(adult, !is.na(socBranch) &
  ##              ((socBranch == "farming" & socStatus == "high") |
##                     (socBranch == "business" & socStatus == "low")
##                ))
##tre <- with(adult, !is.na(socBranch) &
##                    (socBranch == "official" & socStatus == "low")
##               )
tva <- with(adult, !is.na(socBranch) &
                ((socBranch == "farming" & socStatus == "high") |
                 (socBranch == "business" & socStatus == "low") |
                 (socBranch == "official" & socStatus == "low")
                ))

@@

Now let us put on emph{partner} on {\bf lisaold}.

<<partner>>=
load("../../Data/partner.rda")
##females <- lisaold[lisaold$sex == "female", ]
##par.fem <- partner[partner$LINNEID1 %in% females$LINNEID | partner$LINNEID2 %in% females$LINNEID2, ]
partner$id1 <- pmin(partner$LINNEID1, partner$LINNEID2)
partner$id2 <- pmax(partner$LINNEID1, partner$LINNEID2)
partner <- unique(partner[, c("LINNEIDAR", "id1", "id2")])
@

### 2017-08-29 article.Rmd

---
title: Is high social class always beneficial for survival? A study of adults and elderly in Northern Sweden 1851--2013
author: "Sören Edvinsson and Göran Broström"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
    toc_float: yes
bibliography: mybib.bib
documentclass: article
citation-package: natbib
biblio-style: apalike
---

>>>>

---
title: Is high social class always beneficial for survival? A study of adults and elderly in Northern Sweden 1851--2013
author: "Sören Edvinsson and Göran Broström"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
    toc_float: yes
bibliography: mybib.bib
documentclass: article
citation-package: natbib
biblio-style: apalike
---
